Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids

### 2025-05-20 analysis/paper/paper.qmd
updates

---
title: "Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids"
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: html
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-dpi: 600

bibliography: references.bib
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# 遍历文件夹中的文本文件
folder_path <- here("analysis/data/QSY_A")
temp_file_list <- list.files(folder_path, pattern = "\\.txt$")  # 只列出 .txt 文件

@@

# 保存为 CSV
write.csv(benn.output,
          here("analysis/data/benn_output.csv"), row.names = FALSE)
```

@@

```{r}
#| label: fig-myfig
#| fig-cap: "the text of the captions. "
#| fig-height: 4

knitr::include_graphics(here::here("analysis/figures/thefigure.png"))
```

```{r}
#| label: get-data
#| eval: false
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

>>>>

---
title: "Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids"
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: html
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-dpi: 600
bibliography: references.bib
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: console
---

@@

# 遍历文件夹中的文本文件
folder_path <- here("analysis/data/raw_data/QSY_A")
temp_file_list <- list.files(folder_path, pattern = "\\.txt$")  # 只列出 .txt 文件

@@

# 保存为 CSV
write.csv(benn.output,
          here("analysis/data/derived_data/benn_output.csv"), row.names = FALSE)
```

@@

```{r}
#| label: fig-myfig
#| fig-cap: "the text of the captions. "

knitr::include_graphics(here("analysis/figures/1.png"))
```

@fig-myfig shows...
